# Data {#data}

There are many data resources necessary to run the full bifrost capelin assessment. We will split this data chapter into the data needed for maturity parameter estimation and the consumption.

## Maturity data
For the maturity part of bifrost, we need data from the acoustic survey in the Barents sea, processed by StoX. By running the StoX projects, a file called "2_EstimateByPopulation_Category_Reports_Abundance.txt" is produced. At the bottom of this file, you find the following table (example from 2016 survey): 

```{r, echo = FALSE}
cat('
______________________________________________________________________________________________________
Variable: Abundance
EstLayer: 1
Stratum: TOTAL
species: 162035
______________________________________________________________________________________________________
                   age                                          
LenGrp                      0        1        2        3        4   Number  Biomass   Mean W
                                                                     (1E3)  (1E3kg)      (g)
______________________________________________________________________________________________________
7.5-8.0           |    108413  3196550        -        -        -  3304964   5109.9     1.55
8.0-8.5           |         -  2217823        -        -        -  2217823   3783.9     1.71
8.5-9.0           |         -  2823284        -        -        -  2823284   5647.8     2.00
9.0-9.5           |         -  3281410        -        -        -  3281410   8391.2     2.56
9.5-10.0          |         -  6291983        -        -        -  6291983  19246.9     3.06
10.0-10.5         |         -  3159791        -        -        -  3159791  11534.3     3.65
10.5-11.0         |         -  1931237    13811        -        -  1945048   8259.7     4.25
11.0-11.5         |         -  2290788        -        -        -  2290788  12006.9     5.24
11.5-12.0         |         -  2248815    82271        -        -  2331085  14483.6     6.21
12.0-12.5         |         -  4699161   357024        -        -  5056185  36801.5     7.28
12.5-13.0         |         -  1340294   268462        -        -  1608756  13458.5     8.37
13.0-13.5         |         -   706850   763254        -        -  1470104  14119.9     9.60
13.5-14.0         |         -   331121   994703    11299        -  1337122  14680.7    10.98
14.0-14.5         |         -    37247  1871252   169922        -  2078422  28255.4    13.59
14.5-15.0         |         -    29063  1054995    90411        -  1174470  18218.4    15.51
15.0-15.5         |         -    10750  1084263    89633    34848  1219495  21461.7    17.60
15.5-16.0         |         -        -   580099   429271        -  1009370  20859.0    20.67
16.0-16.5         |         -        -   629549   420717    74734  1125000  25230.4    22.43
16.5-17.0         |         -        -   170522   310787     8881   490190  12514.5    25.53
17.0-17.5         |         -        -    55086   531150     5792   592027  17443.1    29.46
17.5-18.0         |         -        -     4998   155824    30239   191061   6166.7    32.28
18.0-18.5         |         -        -        -    96756        -    96756   3606.3    37.27
18.5-19.0         |         -        -     9115    44474        -    53589   1960.2    36.58
19.0-19.5         |         -        -        -     7286        -     7286    324.9    44.59
______________________________________________________________________________________________________
TSN(1000)         |    108413 34596168  7939404  2357530   154495 45156010        -        -
TSB(1000 kg)      |     128.6 144667.9 115752.5  59107.0   3909.2        - 323565.2        -
Mean length (cm)  |      7.50    10.00    14.23    16.19    16.14        -        -        -
Mean weight (g)   |      1.19     4.18    14.58    25.07    25.30        -        -     7.17
______________________________________________________________________________________________________
')
```

This is the information we have stored in the example data *cap* for the years 1972-2019, which you can load by running the following code:

```{r eval = TRUE}
data(cap, package = "bifrost")
head(dplyr::filter(cap, year == 2016), n = 10)
```



