--- 
title: "The bifrost R package"
author: "Sondre Hølleland and Samuel Subbey, Institute of Marine Research, Norway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::gitbook:
    lib_dir: "book_assets"
  bookdown::pdf_book:
    keep_tex: yes
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is the a user-guide to the bifrost R package."
---

# Prerequisites

The R-package **bifrost** is created for doing the capelin assessment. To install the package, you need

* R (preferrably version 4.0.3) and Rtools (4.0)
* R-package *devtools*

Download and install R here: [https://cran.uib.no/](https://cran.uib.no/).

Download and install Rtools 4.0 here: [https://cran.r-project.org/bin/windows/Rtools/](https://cran.r-project.org/bin/windows/Rtools/).
This will install the necessary C++ compiler for using TMB (template model builder). 


```{r eval=FALSE}
# If you don't have devtools: 
install.packages("devtools")
devtools::install_github("holleland/bifrost", dependencies = TRUE)
```

This should also install e.g. TMB. 

**Software used in development and testing**: 

- R version: 4.0.3 
- Rtools version: 4.0
- OS: Windows 10 


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

**Financial support:** 

[Institute of Marine Research](https://www.hi.no) project: 15568 Forvaltningsstrategier for Barentshavet


<img src="https://www.hi.no/en/hi/resources/layout/HI-logo-farger-engelsk.svg/original"
alt="Institute of Marine Research" width="200"/>
